---
title: "Analysis SocCult"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

.libPaths( c("C:/Users/biank/Documents/Skole/CogSci/R_packages", .libPaths() ) )
.libPaths()

library(pacman)
pacman::p_load(tidyverse,brms)
```



```{r, include=FALSE}
#read the two datasets



#merge the two datasets


combined$d_data<-as.numeric(combined$d_data)
combined$q_data<-as.numeric(combined$q_data)
combined$f_data<-as.numeric(combined$f_data)
```


## Template

### Define hypotheses / Describe variables

I will test for the following two hypotheses: 
H1: Corruption rate of one's native country has an effect on interpersonal trust.

H2: The effect declines over time spent in a non-corrupt country like Denmark

Variables involved:

Outcome: 3 different scores of interpersonal trust

- trust_prisoners_dilemma (d_data), 2 rounds times scores 0-1, binomial

- trust_faces (face_data), 20 observation times scores from 1-6
discrete variable, only positive, normally distributed

- trust_questionnaire (q_data), 4 questions scores from 1-6
discrete variable, only positive, normally distributed


Predictors: 

H1:
CPI_native: Corruption Perception Index, a scale from 1-100, where 100 indicates no corruption at all for native country: discrete variable, only positive, 

Condition: dilemma 1 or 2 ; faces 1 - 20; q 1- q4

ID

H2: 
CPI_native
Condition
ID
Years: Number of years spent in current country
CPI_change = CPI_current - CPI_native
            Positive score = Less corruption
            Negative score = more corruption
0 = no change, probably haven’t moved


Other predictors I consider to include to rule out other underlying factors
- Native country GDP
- Highest level of education

I will make the following models:

H1: 

Baseline / m0: Interpersonal trust ~ condition

m1: Interpersonal trust ~ CPI_native + condition,

m2: Interpersonal trust ~ CPI_native + condition + (1 + condition | ID) ,

Each of these for the 3 different outcome variables, so 9 models.


H2: 

m3: Interpersonal trust  ~ 1 + CPI_native + CPI_change + condition CPI_change:Years ,
m4: Interpersonal trust  ~ 1 + CPI_native + CPI_change + condition CPI_change:Years + (1 + condition | ID)

Each of these fir the 3 different outcome variables, so 6 models.



################################## H1 ############################### 

```{r}
# I try to make a multivariate model for H1 basic
#First, I will define my models:
f0<- bf(mvbind(d_data,q_data,face_data) ~ 1 + condition)
f0_d<-bf(d_data ~ d_condition+binomial())
f0_q<-bf(q_data ~  q_condition)
f0_f<-bf(f_data ~ f_condition+gaussian())
f0<-f0_d+f0_q+f0_f

f1<- bf(mvbind(d_data,q_data,face_data) ~ 1 + condition + CPI_native)
f1_d<-bf(d_data ~ 1 + d_condition+CPI_native)
f2<- bf(mvbind(d_data,q_data,face_data) ~ 1 + condition + CPI_native + (1 + condition | ID))
 

```


Define priors and quality check
```{r}
############### prior for dilemma #####################
hist(combined$d_data)
hist(combined$f_data)
get_prior(f0_d, combined, binomial())

f0_d_prior<-c(
  prior(normal(0.5, 0.2), class = Intercept),
  prior(normal(0.2, .1), class = b)
)

f0_d_prior_m <- brm(
  f0_d,
  combined,
  family = binomial,
  prior = f0_d_prior,
  sample_prior = "only",
  chains = 2,
  cores = 3,
  )

pp_check(f0_d_prior_m,nsamples=1000)


############# prior for questionnaire ###################

get_prior(f0_q, combined, gaussian())

f0_q_prior<-c(
  prior(normal(0.5, 0.2), class = Intercept),
  prior(normal(0.2, .1), class = b,
  prior(normal(0.2, .1), class = b,
  prior(normal(0.2, .1), class = b,
  prior(normal(0.2, .1), class = b)
)

f0_d_prior_m <- brm(
  f0_d,
  combined,
  family = binomial,
  prior = f0_d_prior,
  sample_prior = "only",
  chains = 2,
  cores = 3,
  )

pp_check(f0_d_prior_m,nsamples=1000)



f0_d_m <- brm(
  f0_d,
  combined,
  family = binomial(),
  prior = f0_d_prior,
  sample_prior = T,
  chains = 2,
  cores = 3,
  )

pp_check(f0_d_m,nsamples=1000)

summary(f0_d_m)



summary(f0_d_m)


```

```{r}
####### f1d
get_prior(f1_d, combined, family = binomial())

f1_d_prior<-c(
  prior(normal(0.5, 0.2), class = Intercept),
  prior(normal(0.2, .1), class = b, coef=CPI_native),
  prior(normal(0.2, .1), class = b, coef=d_conditionDilemma2)
)

f1_d_prior_m <- brm(
  f1_d,
  combined,
  family = binomial(),
  prior = f1_d_prior,
  sample_prior = "only",
  chains = 2,
  cores = 3,
  )


pp_check(f1_d_prior_m,nsamples=1000)


f1_d_m <- brm(
  f1_d,
  combined,
  family = binomial,
  prior = f1_d_prior,
  sample_prior = T,
  chains = 2,
  cores = 3,
  )

summary(f1_d_m)
```

Make the models + predictive posterior check:
```{r}

```


Visualization of results:
```{r}

```


Model comparisons:
```{r}

```





################################## H2 ############################### 

```{r}
# I try to make a multivariate model for H2 
#First, I will define my models:
f3<- bf(mvbind(d_data,q_data,face_data) ~ 1 + CPI_native + CPI_change + condition CPI_change:Years)

f4<- bf(mvbind(d_data,q_data,face_data) ~ 1 + CPI_native + CPI_change + condition CPI_change:Years + (1 + condition | ID))


```


Define priors and quality check
```{r}
#defining priors and quality check for the models in H2


```


Make the models + predictive posterior check:
```{r}

```


Visualization of results:
```{r}

```


Model comparisons:
```{r}

```

### Identify your model[s] 
* likelihood function
* formula
* priors

### Assess model quality
* Predictive prior checks
* Divergences / Rhat / ESS
* Prior/Posterior learning (betas and sds)
* Model comparison
* Predictive posterior checks

### Report results
* Model comparison
* Estimates and hypothesis testing
* Make sure to deal cautiously with interactions (e.g. plot!)
* Make sure to let the reader know the effects of the estimates on the outcome scale (if generalized linear model)


### Define your hypotheses
People will conform to peer feedback, that is, they will change according to the feedback.

### Describe variables
Outcome: 
- Change (amount of change from the first rating)
Predictors: 
- Feedback (difference between first rating and peer feedback)
- FirstRating (starting point, e.g. if early rating is 8, difficult to go up!)
- ID: participant ID
- FaceID: face ID

### Identify your model[s] 
* likelihood function: Change is numeric and goes from -6 to +6. Roughly gaussian?
* formula: 
* priors

```{r}

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
