---
title: "Analysis SocCult"
output: 
  md_document:
      variant: markdown_github
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

.libPaths( c("C:/Users/biank/Documents/Skole/CogSci/R_packages", .libPaths() ) )
.libPaths()

library(pacman)
pacman::p_load(tidyverse,brms)


```



```{r echo=TRUE}
#read the two datasets
combined_eng <- read_csv("combined_eng.csv")
combined_dan<-read_csv("combined_danish.csv")

#merge the two datasets

combined<-merge(combined_dan, combined_eng,all=T)


combined$d_data<-as.numeric(combined$d_data)
combined$q_data<-as.numeric(combined$q_data)
combined$f_data<-as.numeric(combined$f_data)



#make a column for CPI_change

combined$CPI_change<-combined$CPI_current-combined$CPI_native

set.seed(1999)
```


## Template

### Define hypotheses / Describe variables

I will test for the following two hypotheses: 
H1: Corruption rate of one's native country has an effect on interpersonal trust.

H2: The effect declines over time spent in a non-corrupt country like Denmark

Variables involved:

Outcome: 3 different scores of interpersonal trust

- trust_prisoners_dilemma (d_data), 2 rounds times scores 0-1, binomial

- trust_faces (face_data), 20 observation times scores from 1-6
discrete variable, only positive, normally distributed

- trust_questionnaire (q_data), 4 questions scores from 1-6
discrete variable, only positive, normally distributed


Predictors: 

H1:
CPI_native: Corruption Perception Index, a scale from 1-100, where 100 indicates no corruption at all for native country: discrete variable, only positive, 

Condition: dilemma 1 or 2 ; faces 1 - 20; q 1- q4

ID

H2: 
CPI_native
Condition
ID
Years: Number of years spent in current country
CPI_change = CPI_current - CPI_native
            Positive score = Less corruption
            Negative score = more corruption
0 = no change, probably haven’t moved


Other predictors I consider to include to rule out other underlying factors
- Native country GDP
- Highest level of education

I will make the following models:

H1: 

Baseline / m0: Interpersonal trust ~ condition

m1: Interpersonal trust ~ CPI_native + condition,

m2: Interpersonal trust ~ CPI_native + condition + (1 + condition | ID) ,

Each of these for the 3 different outcome variables, so 9 models.


H2: 

m3: Interpersonal trust  ~ 1 + CPI_native + CPI_change + condition CPI_change:Years ,
m4: Interpersonal trust  ~ 1 + CPI_native + CPI_change + condition CPI_change:Years + (1 + condition | ID)

Each of these fir the 3 different outcome variables, so 6 models.



################################## H1 ############################### 

```{r}

#First, I will define my models:


f0_d<-bf(d_data ~ 1 + d_condition) #bernoulli
f0_q<-bf(q_data ~ 1 + q_condition)#cumulative?
f0_f<-bf(f_data ~ 1 + f_condition) #cumulative


f1_d<-bf(d_data ~ 1 + d_condition+CPI_native)
f1_q<-bf(q_data ~ 1 + q_condition+CPI_native)
f1_f<-bf(f_data ~ 1 + f_condition+CPI_native)


f2_d<-bf(d_data ~ CPI_native + d_condition + (1 + d_condition | ID))
f2_q<-bf(q_data ~ CPI_native + q_condition + (1 + q_condition | ID))
f2_f<-bf(f_data ~ CPI_native + f_condition + (1 + f_condition | ID))


 

```


Making the priors for m0
```{r Priors for Prisoners Dilemma}
############### prior for dilemma #####################
hist(combined$d_data)
hist(combined$f_data)
hist(combined$q_data)

get_prior(f0_d, combined, bernoulli())

f0_d_prior<-c(
  prior(normal(0.5, 0.2), class = Intercept),
  prior(normal(0.2, .1), class = b)
)

f0_d_prior_m <- brm(
  f0_d,
  combined,
  family = bernoulli,
  prior = f0_d_prior,
  sample_prior = "only",
  chains = 2,
  cores = 3,
  file = "d_m0_prior"
  )

pp_check(f0_d_prior_m,nsamples=1000)


####### f1 prior for dilemma ############
get_prior(f1_d, combined, family = bernoulli())

f1_d_prior<-c(
  prior(normal(0.5, 0.2), class = Intercept),
  prior(normal(0.2, .1), class = b, coef=CPI_native),
  prior(normal(0.2, .1), class = b, coef=d_conditionDilemma2)
)

f1_d_prior_m <- brm(
  f1_d,
  combined,
  family = bernoulli(),
  prior = f1_d_prior,
  sample_prior = "only",
  chains = 2,
  cores = 3,
  file = "d_m1_prior"
  )


pp_check(f1_d_prior_m,nsamples=1000)



####### f2 prior for dilemma ############
get_prior(f2_d, combined, family = bernoulli())

f2_d_prior<-c(
  prior(normal(0.5, 0.2), class = Intercept),
  prior(normal(0.2, .1), class = b, coef=CPI_native),
  prior(normal(0.2, .1), class = b, coef=d_conditionDilemma2),
  prior(normal(0, .1), class = sd)
)

f2_d_prior_m <- brm(
  f2_d,
  combined,
  family = bernoulli(),
  prior = f2_d_prior,
  sample_prior = "only",
  chains = 2,
  cores = 3,
  file = "d_m2_prior"
  )


pp_check(f2_d_prior_m,nsamples=100)







```


```{r Prisoners: Models and model comparison}

################## making the models #####################



d_m0 <- brm(
  f0_d,
  combined,
  family = bernoulli(),
  prior = f0_d_prior,
  sample_prior = T,
  chains = 2,
  cores = 3,
  file = "d_m0"
  )

summary(d_m0)




d_m1 <- brm(
  f1_d,
  combined,
  family = bernoulli,
  prior = f1_d_prior,
  sample_prior = T,
  chains = 2,
  cores = 3,
  file = "d_m1"
  )

summary(d_m1)




d_m2 <- brm(
  f2_d,
  combined,
  family = bernoulli,
  prior = f2_d_prior,
  sample_prior = T,
  chains = 2,
  cores = 3,
  file = "d_m2"
  )

summary(d_m2)

d_m0<-add_criterion(d_m0,criterion="loo")
d_m1<-add_criterion(d_m1,criterion="loo")
d_m2<-add_criterion(d_m2,criterion="loo")

loo_compare(d_m0, d_m1, d_m2)
loo_model_weights(d_m0, d_m1, d_m2)
```






```{r Priors for Questionnaire}

############# f0 prior for questionnaire ###################

get_prior(f0_q, combined, family=cumulative)
            
mean(combined$q_data,na.rm=TRUE)
sd(combined$q_data,na.rm=TRUE)
f0_q_prior<-c(
  prior(normal(3.5, 1), class = Intercept),
  prior(normal(0.5, .2), class = b)
  )


f0_q_prior_m <- brm(
  f0_q,
  combined,
  family = cumulative(),
  prior = f0_q_prior,
  sample_prior = "only",
  chains = 2,
  cores = 3,
  file = "q_m0_prior"
  )

pp_check(f0_q_prior_m,nsamples=100)





####################### f1 prior for questionnaire ####################

get_prior(f1_q, combined, family=cumulative)

f1_q_prior<-c(
  prior(normal(3.5, 1), class = Intercept),
  prior(normal(0.3, .1), class = b),
  prior(normal(0.3, .1), class = b,coef=q_conditionQ2),
  prior(normal(0.3, .1), class = b,coef=q_conditionQ3),
  prior(normal(0.3, .1), class = b,coef=q_conditionQ4),
  prior(normal(0.3, .1), class = b,coef=CPI_native)
  )


f1_q_prior_m <- brm(
  f1_q,
  combined,
  family=cumulative,
  prior = f1_q_prior,
  sample_prior = "only",
  chains = 2,
  cores = 3,
  file = "q_m1_prior"
  )

pp_check(f1_q_prior_m,nsamples=100)



####################### f2 prior for questionnaire ####################

get_prior(f2_q, combined, family=cumulative)

f2_q_prior<-c(
  prior(normal(3.5, 1), class = Intercept),
  prior(normal(0.3, .1), class = b),
  prior(normal(0.3, .1), class = b,coef=CPI_native),
  prior(normal(0.3, .1), class = b,coef=q_conditionQ2),
  prior(normal(0.3, .1), class = b,coef=q_conditionQ3),
  prior(normal(0.3, .1), class = b,coef=q_conditionQ4),
  prior(normal(0, .1), class = sd)
  )


f2_q_prior_m <- brm(
  f2_q,
  combined,
  family=cumulative,
  prior = f2_q_prior,
  sample_prior = "only",
  chains = 2,
  cores = 3,
  file = "q_m2_prior"
  )

pp_check(f2_q_prior_m,nsamples=100)





```

```{r Questionnaire models and comparisons }

q_m0 <- brm(
  f0_q,
  combined,
  family = cumulative,
  prior = f0_q_prior,
  sample_prior = T,
  chains = 2,
  cores = 3,
  file = "q_m0"
  )

summary(q_m0)

q_m1 <- brm(
  f1_q,
  combined,
  family=cumulative,
  prior = f1_q_prior,
  sample_prior = T,
  chains = 2,
  cores = 3,
  file = "q_m1"
  )

summary(q_m1)

q_m2 <- brm(
  f2_q,
  combined,
  family=cumulative,
  prior = f2_q_prior,
  sample_prior = T,
  chains = 2,
  cores = 3,
  file = "q_m2"
  )

summary(q_m2)


q_m0<-add_criterion(q_m0,criterion="loo")
q_m1<-add_criterion(q_m1,criterion="loo")
q_m2<-add_criterion(q_m2,criterion="loo")

loo_compare(q_m0, q_m1, q_m2)
loo_model_weights(q_m0, q_m1, q_m2)
```



```{r Faces Priors }

###################### f0 prior for faces ##################################

get_prior(f0_f, combined, family=cumulative)

f0_f_prior<-c(
  prior(normal(3.5, 1), class = Intercept),
  prior(normal(1, .3), class = b)
  )


f0_f_prior_m <- brm(
  f0_f,
  combined,
  family=cumulative,
  prior = f0_f_prior,
  sample_prior = "only",
  chains = 2,
  cores = 3,
  file = "f_m0_prior"
  )

pp_check(f0_f_prior_m,nsamples=100)



####################### f1 prior for faces ############################


get_prior(f1_f, combined, family=cumulative)
mean(combined$f_data,na.rm=TRUE)
sd(combined$f_data,na.rm=TRUE)
f1_f_prior<-c(
  prior(normal(3.5, 1), class = Intercept),
  prior(normal(0.5, .3), class = b),
  prior(normal(0.3, .1), class = b, coef=CPI_native)
  )


f1_f_prior_m <- brm(
  f1_f,
  combined,
  family = cumulative,
  prior = f1_f_prior,
  sample_prior = "only",
  chains = 2,
  cores = 3,
  file = "f_m1_prior"
  )

pp_check(f1_f_prior_m,nsamples=100)


####################### f2 prior for faces ############################


get_prior(f2_f, combined, cumulative())
mean(combined$f_data,na.rm=TRUE)
sd(combined$f_data,na.rm=TRUE)

f2_f_prior<-c(
  prior(normal(3.5, 1), class = Intercept),
  prior(normal(0.5, .3), class = b),
  prior(normal(0.3, .1), class = b, coef=CPI_native),
  prior(normal(0, .1), class = sd)
  )


f2_f_prior_m <- brm(
  f2_f,
  combined,
  family = cumulative,
  prior = f2_f_prior,
  sample_prior = "only",
  chains = 2,
  cores = 3,
  file = "f_m2_prior"
  )

pp_check(f2_f_prior_m,nsamples=100)







```


```{r Faces Models and comparisons}

########################## making the models #################################


f_m0 <- brm(
  f0_f,
  combined,
  family=cumulative(),
  prior = f0_f_prior,
  sample_prior = T,
  chains = 2,
  cores = 3,
  file = "f_m0"
  )

pp_check(f_m0,nsamples=100)
summary(f_m0)

f_m1 <- brm(
  f1_f,
  combined,
  family=cumulative(),
  prior = f1_f_prior,
  sample_prior = T,
  chains = 2,
  cores = 3,
  file = "f_m1"
  )

pp_check(f_m1, nsamples=100)
summary(f_m1)

f_m2 <- brm(
  f2_f,
  combined,
  family=cumulative(),
  prior = f2_f_prior,
  sample_prior = T,
  chains = 2,
  cores = 3,
  file = "f_m2"
  )

pp_check(f_m2,nsamples=100)
summary(f_m2)


f_m0<-add_criterion(f_m0,criterion="loo")
f_m1<-add_criterion(f_m1,criterion="loo")
f_m2<-add_criterion(f_m2,criterion="loo")

loo_compare(f_m0, f_m1, f_m2)
loo_model_weights(f_m0, f_m1, f_m2)
```





Visualization of results:
```{r Hypothesis testing H1}

plot(hypothesis(d_m1,"CPI_native > 0"))
hypothesis(d_m1,"CPI_native > 0")


plot(hypothesis(q_m1,"CPI_native > 0"))
hypothesis(q_m1,"CPI_native > 0")


plot(hypothesis(f_m1,"CPI_native > 0"))
hypothesis(f_m1,"CPI_native > 0")


plot(hypothesis(d_m2,"CPI_native > 0"))
hypothesis(d_m2,"CPI_native > 0")

plot(hypothesis(q_m2,"CPI_native > 0"))
hypothesis(q_m2,"CPI_native > 0")

plot(hypothesis(f_m2,"CPI_native > 0"))
hypothesis(f_m2,"CPI_native > 0")

plot(f_m2)

```


Model comparisons:
```{r}

```





################################## H2 ############################### 

```{r Models for H2}



f3_d<- bf(d_data ~ 1 + CPI_native + CPI_change + d_condition + CPI_change * Years_Current + (1 + d_condition | ID))

f3_q<- bf(q_data ~ 1 + CPI_native + CPI_change + q_condition + CPI_change * Years_Current + (1 + q_condition | ID))

f3_f<- bf(f_data ~ 1 + CPI_native + CPI_change + f_condition + CPI_change * Years_Current + (1 + f_condition | ID))

```



```{r Priors for Prisoners Dilemma}
############### prior for dilemma #####################

get_prior(f3_d, combined, bernoulli())

f3_d_prior<-c(
  prior(normal(0.5, 0.2), class = Intercept),
  prior(normal(0.2, .1), class = b, coef=CPI_native),
  prior(normal(0.2, .1), class = b, coef=d_conditionDilemma2),
  prior(normal(0.2, .1), class = b, coef=Years_Current),
  prior(normal(0.2, .1), class = b, coef=CPI_change:Years_Current),
  prior(normal(0, .1), class = sd)
)


f3_d_prior_m <- brm(
  f3_d,
  combined,
  family = bernoulli,
  prior = f3_d_prior,
  sample_prior = "only",
  chains = 2,
  cores = 3,
  file = "d_m3_prior"
  )

pp_check(f3_d_prior_m,nsamples=1000)



```


```{r Prisoners: Models and model comparison}

################## making the models #####################



d_m3 <- brm(
  f3_d,
  combined,
  family = bernoulli(),
  prior = f3_d_prior,
  sample_prior = T,
  chains = 2,
  cores = 3,
  file = "d_m3"
  )

summary(d_m3)



d_m3<-add_criterion(d_m3,criterion="loo")


loo_compare(d_m0, d_m1, d_m2, d_m3)
loo_model_weights(d_m0, d_m1, d_m2, d_m3)
```






```{r Priors for Questionnaire}

############# f0 prior for questionnaire ###################

get_prior(f3_q, combined, cumulative())


f3_q_prior<-c(
  prior(normal(3.5, 1), class = Intercept),
  prior(normal(0.3, .1), class = b),
  prior(normal(0.3, .1), class = b,coef=CPI_native),
  prior(normal(0, .1), class = sd),
  prior(normal(0.2, .1), class = b, coef=Years_Current),
  prior(normal(0.2, .1), class = b, coef=CPI_change:Years_Current)
  )


f3_q_prior_m <- brm(
  f3_q,
  combined,
  family = cumulative,
  prior = f3_q_prior,
  sample_prior = "only",
  chains = 2,
  cores = 3,
  file = "q_m3_prior"
  )

pp_check(f3_q_prior_m,nsamples=100)





```

```{r Questionnaire models and comparisons }

q_m3 <- brm(
  f3_q,
  combined,
  family = cumulative,
  prior = f3_q_prior,
  sample_prior = T,
  chains = 2,
  cores = 3,
  file = "q_m3"
  )

summary(q_m3)



q_m3<-add_criterion(q_m3,criterion="loo")
q_m0<-ass_criterion(q_m0, criterion="loo")

loo_compare(q_m0, q_m1, q_m2, q_m3)
loo_model_weights(q_m0, q_m1, q_m2, q_m3)
```



```{r Faces Priors }



####################### f3 prior for faces ############################


get_prior(f3_f, combined, cumulative())

f3_f_prior<-c(
  prior(normal(3.7, 1), class = Intercept),
  prior(normal(0.5, .3), class = b),
  prior(normal(0.3, .1), class = b, coef=CPI_native),
  prior(normal(3.7, 1), class = sigma),
  prior(normal(0.5, .3), class = sd),
  prior(normal(0.2, .1), class = b, coef=Years_Current),
  prior(normal(0.2, .1), class = b, coef=CPI_change:Years_Current)
  )


f3_f_prior_m <- brm(
  f3_f,
  combined,
  family = cumulative,
  prior = f3_f_prior,
  sample_prior = "only",
  chains = 2,
  cores = 3,
  file = "f_m3_prior"
  )

pp_check(f3_f_prior_m,nsamples=100)







```


```{r Faces Models and comparisons}

########################## making the models #################################


f_m3 <- brm(
  f3_f,
  combined,
  family=cumulative(),
  prior = f3_f_prior,
  sample_prior = T,
  chains = 2,
  cores = 3,
  file = "f_m3"
  )

pp_check(f_m3,nsamples=100)
pp_check(q_m3, nsamples=100)
pp_check(d_m3, nsamples=100)
summary(f_m3)


f_m3<-add_criterion(f_m3,criterion="loo")


loo_compare(f_m0, f_m1, f_m2, f_m3)
loo_model_weights(f_m0, f_m1, f_m2, f_m3)
```







Visualization of results:
```{r Hypothesis tests H2}

plot(hypothesis(d_m3,"CPI_change:Years_Current > 0"))
hypothesis(d_m3,"CPI_change:Years_Current > 0")


plot(hypothesis(q_m3,"CPI_change:Years_Current > 0"))
hypothesis(q_m3,"CPI_change:Years_Current > 0")


plot(hypothesis(f_m3,"CPI_change:Years_Current > 0"))
hypothesis(f_m3,"CPI_change:Years_Current > 0")




```




### Identify your model[s] 
* likelihood function
* formula
* priors

### Assess model quality
* Predictive prior checks
* Divergences / Rhat / ESS
* Prior/Posterior learning (betas and sds)
* Model comparison
* Predictive posterior checks

### Report results
* Model comparison
* Estimates and hypothesis testing
* Make sure to deal cautiously with interactions (e.g. plot!)
* Make sure to let the reader know the effects of the estimates on the outcome scale (if generalized linear model)


### Define your hypotheses
People will conform to peer feedback, that is, they will change according to the feedback.

### Describe variables
Outcome: 
- Change (amount of change from the first rating)
Predictors: 
- Feedback (difference between first rating and peer feedback)
- FirstRating (starting point, e.g. if early rating is 8, difficult to go up!)
- ID: participant ID
- FaceID: face ID

### Identify your model[s] 
* likelihood function: Change is numeric and goes from -6 to +6. Roughly gaussian?
* formula: 
* priors

```{r}

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
